Growing Up with Nell: A Narrative Interface for Literacy

### 2012-03-15 paper.tex
Describe the JSON translation of AIML.  It's Alan Kay's fault.

\begin{figure}\small
\begin{verbatim}
{ aiml: {
  version: "1.0",
  categories: [
    { pattern: "GO *",
      template: "{*}" },
    { pattern: "N",
      template: "{NORTH}" },
    { pattern: "NORTH",
      template: js`FireEvent(Chat, "NORTH")` },
    { pattern: "* THE DOOR",
      template: "{*} DOOR" },
    { pattern: "* SQUEAKY DOOR",
      template: "{*} DOOR" },
    { pattern: "OPEN DOOR",
      template: js`FireEvent(Chat, "OPEN DOOR")` }
  ] } }
\end{verbatim}
\caption{An AIML fragment which recognizes the commands \texttt{N},
  \texttt{North}, \texttt{Go North}, \texttt{Open the squeaky door}
  and variants.  AIML's XML format has been translated to JSON.
  Template contents in braces invoke the recognizer recursively.
% XXX: how to handle multiple stars?  In XML, it's <star index="1">
}\label{fig:aiml}
\end{figure}

Our implementation extends AIML~\cite{aiml:2005},
the markup language developed for the Loebner Prize--winning
AliceBot.%
\footnote{Wilcox identifies several shortcomings with the expressive
  power of AIML, proposing ChatScript as a
  replacement~\cite{wilcox:2010}.  AIML's community and
  diversity of third-party implementations make it our choice at present.}
Each story module can include AIML fragments extending the
conversational capabilities of Nell's agents.

@@

We have developed a block-oriented view of JavaScript, which we call
TurtleScript~\cite{turtlescript}.
The TurtleScript dialect of JavaScript is the single
implementation language for Nell.  TurtleScript scales from Logo-like
pedagogical tasks (in subsets of the language) up to the
implementation of TurtleScript and the
Nell system itself.  As Figure~\ref{fig:turtlescript} shows,
TurtleScript's block view is isomorphic to
JavaScript's standard textual
representation to preserve the code-reading skills of existing
programmers.  We have begun implementation of a
tablet programming environment for TurtleScript which uses
drag-and-drop, direct interaction, and intelligent prompting to reduce
text entry requirements.

>>>>

\begin{figure}\small
\begin{verbatim}
{ aiml: {
  version: "1.0",
  categories: [
    { pattern: "GO *",
      template: "{*}" },
    { pattern: "N",
      template: "{NORTH}" },
    { pattern: "NORTH",
      template: js`FireEvent(Chat, "NORTH")` },
    { pattern: "* THE DOOR",
      template: "{*} DOOR" },
    { pattern: "* SQUEAKY DOOR",
      template: "{*} DOOR" },
    { pattern: "OPEN DOOR",
      template: js`FireEvent(Chat, "OPEN DOOR")` }
  ] } }
\end{verbatim}
\caption{An AIML fragment which recognizes the commands
  %\texttt{N},
  \texttt{North}, \texttt{Go North}, \texttt{Open the squeaky door}
  and variants.  AIML's XML syntax has been translated to JSON.
  Template contents in braces invoke the recognizer recursively
  (what AIML calls \texttt{<srai>}).
% XXX: how to handle multiple stars?  In XML, it's <star index="1">
}\label{fig:aiml}
\end{figure}

Our implementation extends AIML~\cite{aiml:2005},
the markup language developed for the Loebner Prize--winning
AliceBot.%
\footnote{Wilcox identifies several shortcomings with the expressive
  power of AIML, proposing ChatScript as a
  replacement~\cite{wilcox:2010}.  AIML's community and
  diversity of third-party implementations make it our choice at present.}
Each story module can include AIML fragments extending the
conversational capabilities of Nell's agents.
% we say this in the figure, don't repeat it here? ==>
%    We have translated AIML's XML-based syntax to JSON.

@@

We have developed a block-oriented view of JavaScript, which we call
TurtleScript~\cite{turtlescript}.
The TurtleScript dialect of JavaScript is the single
implementation language for Nell.%
\footnote{Since JSON is the data-oriented subset of JavaScript,
our examples in Figures~\ref{fig:rules} and \ref{fig:aiml} are valid
TurtleScript.} % XXX: use TurtleScript tiles for the figures?
TurtleScript scales from Logo-like
pedagogical tasks (in subsets of the language) up to the
implementation of TurtleScript and the
Nell system itself.  As Figure~\ref{fig:turtlescript} shows,
TurtleScript's block view is isomorphic to
JavaScript's standard textual
representation to preserve the code-reading skills of existing
programmers.  We have begun implementation of a
tablet programming environment for TurtleScript which uses
drag-and-drop, direct interaction, and intelligent prompting to reduce
text entry requirements.
